GIT-SVN basic commands

### 2013-05-06 doc/Version_Control/Git-SVN_Quick_Reference.tex
Additional directions for git-svn. How to merge in a clean way. 	modified:   Git-SVN_Quick_Reference.tex

>>>>

Merging a development branch into the trunk. The master branch should be merged
beforehand into your development branch. This way the conflicts will only
occure in the developement branch. This also helps to contribute with
up-to-date modifications. Therefore, the following steps should be followed:
\begin{enumerate}
  \item \verb|git checkout master| -- Switch to the \texttt{master}.
  \item \verb|git svn rebase| -- The \texttt{master} is now up-to-date with the repository.
  \item \verb|git checkout mybranch| -- Switch to the branch you want to merge.
  \item \verb|git merge master| -- Update \texttt{mybranch} with the
\texttt{master}. When using git only \verb|--squash| is an option to bundle
multiple modifications in a single one. When using git-svn, it is important to
use the \verb|--no-ff| option, otherwise git will loose branch information.
  \item \verb|git mergetool| -- If there is any conflict to solve.
  \item \verb|git commit| -- Commit the merge.
  \item \verb|git checkout master| -- Switch to the \texttt{master}.
  \item \verb|git merge [--no-ff] branch| -- Update the \texttt{master} with \texttt{mybranch}.
  \item \verb|git commit| -- Commit the merge.
  \item \verb|git svn dcommit| -- Send the merge to the svn repository.
\end{enumerate}
